### 2025-04-13 basic-statistics.qmd
20250413 - add header

You can use the following web application to visualize various distributions according to a specified [center](#sec-descriptiveStatisticsCenter) (mean), [spread](#sec-descriptiveStatisticsSpread) (standard deviation), and [shape](#sec-descriptiveStatisticsShape) (skewness and kurtosis).
Try varying the standard deviation, skewness, and kurtosis to see the impact of each.

>>>>

### Interactive Visualization {#sec-descriptiveStatisticsVisualization}

You can use the following interactive graph to visualize various distributions according to a specified [center](#sec-descriptiveStatisticsCenter) (mean), [spread](#sec-descriptiveStatisticsSpread) (standard deviation), and [shape](#sec-descriptiveStatisticsShape) (skewness and kurtosis).
Try varying the standard deviation, skewness, and kurtosis to see the impact of each.
